### 2013-06-15 replies.tex
Biblio+figure2+text corrections

@@

@@

@@

@@

>>>>

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
accordingly by replacing the abbrevation B by M}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al. (2010), does not allow to evaluate the parameters of a new species entering the community, neither the metaweb (which is the object of the current study). It is therefore not possible to infer the potential links an immigrating species will do with the resident species. These methods also require a complete knowledge of the interactions in the community. Our method is consequently much more robust than previous methods to infer the parameters of the niche model. Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{ We replaced the word "emergent" by "novel".}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%. }}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly and apologize for the mistake}}
